---
title: "Agile Notes"
output:
  html_document:
    df_print: paged
bibliography: bibliography.bib
link-citations: true
---

```{r load packes, include=FALSE}

library(tidyverse)

```



# Agile Notes

## Planen
### Warum planen?
<!-- TODO Investition und Finanzierung Fachbuch: Wann ist eine Investition rentabel? -->
Planen ist aufwendig und führt doch nicht zu den gewünschten Ergebnissen. Warum dann überhaupt planen?

#### The cone of uncertanty
Zeigt, dass Schätzen schwierig ist, Je früher im Prüject desto unsicherer die Schätzung

>The cone of uncertainty shows that during the feasibility phase of
a project a schedule estimate is typically as far off as 60% to 160%. That is, a
project expected to take 20 weeks could take anywhere from 12 to 32 weeks. Af-
ter the requirements are written, the estimate might still be off +/- 15% in either
direction. So an estimate of 20 weeks means work that takes 17 to 23 weeks. 


[@cohn2005agile, 4]


```{r con of uncertainty, echo=FALSE}
coneOfUncertainty <- tibble(status = c("Innitial Product Definition", "Approved Product Definition", "Requirement Specification", "Product Design Specification", "Detailed Design Specification", "Accepted Software"),
                            min = c(0.6, 0.8, 0.85, 0.9, 0.95, 1),
                            max = c(1.6, 1.25, 1.15, 1.1, 1.05, 1)
)

coneOfUncertainty$status <- as.character(coneOfUncertainty$status)
coneOfUncertainty$status <- factor(coneOfUncertainty$status, levels=unique(coneOfUncertainty$status))

ggplot(coneOfUncertainty, mapping = aes(status, max)) +
  geom_point() +
  geom_point(aes(status, min)) +
  theme(axis.text.x = element_text(angle = 45)) 
  
```

### Gründe warum planen
* Reducing risk
  - Risiken durch Planung aufdecken
  - Die größten Risiken erkennen
  - Entscheidungen aufgrund der Risiken treffen
* Reducing uncertainty

> Throughout a project, the team is generating new capabilities in the product. They are also generating new knowledge—about the product, the technologies in use, and themselves as a team. It is critical that this new knowledge be ac- knowledged and factored into an iterative planning process that is designed to help a team refine their vision of the product.

* Supporting better decision making

> Many of the decisions made while planning a project are tradeoff decisions. For example, on every project we make tradeoff decisions between development time and cost. Often the cheapest way to develop a system would be to hire one good programmer and allow her ten or twenty years to write the system, allow- ing her years of detouring to perhaps master the domain, become an expert in database administration, and so on. Obviously, though, we can rarely wait twenty years for a system, and so we engage teams. A team of thirty may spend a year (thirty person-years) developing what a lone programmer could have done in twenty. The development cost goes up, but the value of having the application nineteen years earlier justifies the increased cost.

* Establishing trust
* Conveying information

[@cohn2005agile, 5]

## Schätzen

# References
